Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-01-29 paper.tex
Item 31: Reworded caption for figure 11

\begin{figure}
    \begin{center}
        \includegraphics{graphics/faradaic_currentVsVoltage_IEEE}
    \end{center}
    \caption{Simulated and measured response of the interface model to increasing voltage steps. Measurement points show current values taken at the $64^{th}$ second after each voltage increment.}
    \label{fig:faradaic_currentVsVoltage}
\end{figure}

@@

12. Fig 11 legend ``Simulated and measured response of the interface model''. Surely you mean ``Simulated response of the interface model compared to measurement from the electrodes''?\\
{\color{OliveGreen}
    Item 31\\
    {\color{Red} Yes, this is better. Replace with this.}
    No response yet.
}\\

>>>>

\begin{figure}
    \begin{center}
        \includegraphics{graphics/faradaic_currentVsVoltage_IEEE}
    \end{center}
    \caption{Simulated response of the interface model compared to measurement from the electrodes with a stepped voltage overpotential. Measurement points show current values taken at the $64^{th}$ second after each voltage increment.}
    \label{fig:faradaic_currentVsVoltage}
\end{figure}

@@

12. Fig 11 legend ``Simulated and measured response of the interface model''. Surely you mean ``Simulated response of the interface model compared to measurement from the electrodes''?\\
{\color{OliveGreen}
    Item 31\\
    {\color{Red} Yes, this is better. Replace with this.}
    Yes, that is better - thank you.
}\\
